Hyperopt-Sklearn: Subtitle?

### 2014-04-26 papers/2014-automl/paper.tex

The configuration space we experiment on below includes five preprocessing algorithms and seven classification algorithms.
The full search space is illustrated in Figure~\ref{fig:searchspace}.
The preprocessing algorithms were (by class name, followed by n. hyperparameters + n. unused hyperparameters): \texttt{PCA}(2), \texttt{StandardScaler}(2), \texttt{MinMaxScaler}(1), \texttt{Normalizer}(1), and \texttt{TF-IDF}(0+9).
The first four preprocessing algorithms were for dense features.
PCA performed whitening or non-whitening principle components analysis.
The \texttt{StandardScaler}, \texttt{MinMaxScaler}, and \texttt{Normalizer} did various feature-wise affine transforms to map numeric input features onto values near 0 and with roughly unit variance.
The \texttt{TF-IDF} pre-processing module performed feature extraction from text data.
The classification algorithms were (by class name (used + unused hyperparameters)): \texttt{SVC}(23), \texttt{LinearSVC}, \texttt{KNN}(4+5), \texttt{RandomForest}(8, \texttt{ExtraTrees}(8), \texttt{SGD}(8+4), and \texttt{MultinomialNB}(2).
The \texttt{SVC} module is a fork of LibSVM, and our wrapper has 23 hyperparameters because we treated each possible kernel as a different classifier, with its own set of hyperparameters: Linear(4), RBF(5), Polynomial(7), and Sigmoid(6).

In total, our parameterization had 62 hyperparameters: 6 for preprocessing and 56 for classification.
How many boolean: XXX
How many categorical: XXX
How many discrete: XXX
How many real-valued: XXX
It is important to note that although the total number of hyperparameters is large, the number of {\em active} hyperparameters describing any one model is much smaller: a model consisting of \texttt{PCA} and a \texttt{RandomForest} for example,
would have only 12 active hyperparameters (1 for the choice of preprocessing, 2 internal to PCA, 1 for the choice of classifier and 8 internal to the RF).
Hyperopt description language allows us to differentiate between {\em conditional} hyperparameters (which must always be assigned) and {\em non-conditional} hyperparameters (which may remain unassigned when they would be unused).
We make use of this mechanism extensively so that Hyperopt's search algorithms do not waste time learning by trial and error that e.g. RF hyperparameters have no effect on SVM performance.
Even within a single classifier, there were instances of conditional parameters: \texttt{KNN} has conditional parameters depending on the distance metric,
and \texttt{LinearSVC} has 3 binary parameters (``loss'', ``penalty'', and ``dual'') that admit only 4 valid joint assignments.
We also included a blacklist of (preprocessing, classifier) pairs that did not work together, e.g. PCA and MinMaxScaler were incompatible with MultinomialNB, TF-IDF could only be used for text data, and the tree-based classifiers were not
compatible with the sparse features produced by the TF-IDF preprocessor.
Allowing for a 10-way discretization of real-valued hyperparameters, and taking these conditional hyperparameters into account, a grid search of our search space would still require an infeasible number of evalutions (on the order of $10^{12}$).

@@

\begin{figure}
    \centering
    \includegraphics[width=2.90in]{AverageTestScoresClassifier}
    \caption{
        For each data set, searching the full configuration space (``Any Classifier'') delivered performance approximately on par with a search that was restricted to the best classifier type.
        (Best viewed in color.)
    }
    \label{fig:avg_test_scores}
%\vspace{-3em}
\end{figure}

>>>>

The configuration space we experiment on below includes five preprocessing algorithms and seven classification algorithms.
The full search space is illustrated in Figure~\ref{fig:searchspace}.
The preprocessing algorithms were (by class name, followed by n. hyperparameters + n. unused hyperparameters): \texttt{PCA}(2), \texttt{StandardScaler}(2), \texttt{MinMaxScaler}(1), \texttt{Normalizer}(1), and \texttt{TF-IDF}(0+9).
The first four preprocessing algorithms were for dense features.
PCA performed whitening or non-whitening principle components analysis.
The \texttt{StandardScaler}, \texttt{MinMaxScaler}, and \texttt{Normalizer} did various feature-wise affine transforms to map numeric input features onto values near 0 and with roughly unit variance.
The \texttt{TF-IDF} pre-processing module performed feature extraction from text data.
The classification algorithms were (by class name (used + unused hyperparameters)): \texttt{SVC}(23), \texttt{LinearSVC}(6), \texttt{KNN}(4+5), \texttt{RandomForest}(8), \texttt{ExtraTrees}(8), \texttt{SGD}(8+4), and \texttt{MultinomialNB}(2).
The \texttt{SVC} module is a fork of LibSVM, and our wrapper has 23 hyperparameters because we treated each possible kernel as a different classifier, with its own set of hyperparameters: Linear(4), RBF(5), Polynomial(7), and Sigmoid(6).

In total, our parameterization had 65 hyperparameters: 6 for preprocessing and 59 for classification.
How many boolean: 15
How many categorical: 14
How many discrete: 17
How many real-valued: 19
It is important to note that although the total number of hyperparameters is large, the number of {\em active} hyperparameters describing any one model is much smaller: a model consisting of \texttt{PCA} and a \texttt{RandomForest} for example,
would have only 12 active hyperparameters (1 for the choice of preprocessing, 2 internal to PCA, 1 for the choice of classifier and 8 internal to the RF).
Hyperopt description language allows us to differentiate between {\em conditional} hyperparameters (which must always be assigned) and {\em non-conditional} hyperparameters (which may remain unassigned when they would be unused).
We make use of this mechanism extensively so that Hyperopt's search algorithms do not waste time learning by trial and error that e.g. RF hyperparameters have no effect on SVM performance.
Even within a single classifier, there were instances of conditional parameters: \texttt{KNN} has conditional parameters depending on the distance metric,
and \texttt{LinearSVC} has 3 binary parameters (``loss'', ``penalty'', and ``dual'') that admit only 4 valid joint assignments.
We also included a blacklist of (preprocessing, classifier) pairs that did not work together, e.g. PCA and MinMaxScaler were incompatible with MultinomialNB, TF-IDF could only be used for text data, and the tree-based classifiers were not
compatible with the sparse features produced by the TF-IDF preprocessor.
Allowing for a 10-way discretization of real-valued hyperparameters, and taking these conditional hyperparameters into account, a grid search of our search space would still require an infeasible number of evalutions (on the order of $10^{12}$).

@@

\begin{figure}
    \centering
    \includegraphics[width=2.90in]{graphics/AverageTestScoresClassifiersTPE}
    \caption{
        For each data set, searching the full configuration space (``Any Classifier'') delivered performance approximately on par with a search that was restricted to the best classifier type.
        (Best viewed in color.)
    }
    \label{fig:avg_test_scores}
%\vspace{-3em}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/scores_by_classifier}
    \caption{
	    XXX
    }
    \label{fig:per_clf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/scores_per_eval}
    \caption{
	    XXX
    }
    \label{fig:per_eval}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/AvgMinValidErrorTPE}
    \caption{
	    XXX
    }
    \label{fig:errtpe}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/newsgroups_pie}
    \caption{
	    XXX
    }
    \label{fig:npie}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/mnist_pie}
    \caption{
	    XXX
    }
    \label{fig:mpie}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/convex_pie}
    \caption{
	    XXX
    }
    \label{fig:cpie}
\end{figure}
